DeepPicar: A Low-cost Deep Neural Network-based Autonomous Car

### 2018-01-29 paper/evaluation.tex
Minor change to evaluation sections
Update PALLOC multicore experiment
Updated Figure 12 with the new data

In this experiment, we launch multiple instances of DeepPicar's DNN
model at the same time and measure its impact on their inference
timings. In other words, we are interested in how shared resource
contention affects inference timing.

@@

The results can be seen in Figures \ref{fig:palloc_multicore} - 
\ref{fig:palloc_bandwidth_l2missrate}. As 
expected, based off of previous results, we find that the performance 
of the DNN remains consistent when cache partitioning is employed. 
When fewer cores are used, DNN performance is slightly affected as 
the entire L2 cache isn't available to the network. In the case of 
running multiple models simultaneously, no performance improvements 
are seen, which further shows that the shared cache has little affect on 
the DNN's real-time performance.

In the case of running the DNN alongside synthetic memory-intensive 
benchmarks, however, we found that partitioning the L2 cache led to a 
decrease in performance as the number of co-runners increased. 
However, the L2 miss rates of the model decrease as more benchmarks 
are introduced. As such, this means that the model encounters greater 
interence from the memory contention of the co-runners.

By partitioning the shared L2 cache, we find that no noticable 
improvements are gained and that performance remains consistent, or 
decreases, depending on the circumstances. As a result, we conclude that 
cache partitioning is not an effective isolation mechanism, and that 
the performance of the shared DRAM controller is of greater importance 
to the real-time efficiacy of the DeepPicar.

>>>>

In this experiment, we launch multiple instances of DeepPicar's DNN
model at the same time and measure its impact on their inference
timings. In other words, we are interested in how shared resource
contention affects inference timing. These instances are not identical
copies of the same model, but are instead copies of different models. 
This is done to ensure that no L2 cache memory is shared between the 
models as they are running.

@@

We run the DNN model with different amounts of L2 cache being
available based on the number of colors being used. For example, if two 
colors are used, then 25\% of the L2 cache is available, whereas if all 
8 colors are used, 100\% of the L2 cache is available. Particularly, we 
test the performance of the model when it utilizes a single core and
all four of the available cores. The results can be seen in 
\ref{fig:palloc_multicore}. As expected, the amount of L2 cache 
available to the model does not result in any significant changes in 
performance. As such, we find that a single model is not sensitive to 
the shared L2 cache.

We also co-schedule multiple models to see how cache partitioning affects
interference between them. Each model uses an equal number of colors, and
are thus given equal amounts of L2 cache space, and there is no overlap
in the colors used, so no L2 cache is shared between models. As can be 
seen in \ref{fig:palloc_multimodel}, the performance of the models 
remains the same as when no cache partitioning was employed. Based of 
these results, we find that contention for the L2 cache is not the main
source of interference between multiple DNN models.

Finally, we run a single model alongside memory intensive co-runners 
again, but ensure that each task is given equal amounts of L2 cache space.
For this, we assign two colors to each task, regardless of the number of
tasks being scheduled. As a result, the entire cache is not utilized in
experiments with less than four tasks. The results can be seen in 
\ref{fig:palloc_bandwidth_exectime}. With zero or one co-runners, the DNN
performance doesnt't change relative to when the cache wasn't partitioned.
However, we find that with two or more co-runners, DNN performance becomes
worse. In the case of two co-runners, average control loop time increases
by 66.31 ms, or 26\%, and with three co-runners, the average time
is 265.64 ms, of 49\%, greater.

%TODO: Talk about the prefetcher, or something, for why the benchmark performance is worse.

By partitioning the shared L2 cache, we find that no noticable 
improvements are gained and that performance remains consistent, or 
decreases, depending on the circumstances. In all experiements, the DNN
shows no sensitivity to the shared L2 cache. As a result, we conclude 
that cache partitioning is not an effective isolation mechanism, and that 
the performance of the shared DRAM controller is of greater importance 
to the real-time efficiacy of the DeepPicar.
